\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{amsmath}

% Color and Link setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

% Page styling setup
\pagestyle{empty}
\setlist[itemize]{noitemsep, topsep=2pt, parsep=1pt, partopsep=0pt}

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\begin{document}

% HEADER
\begin{center}
    {\Huge \textbf{ADRIAN BELTRAN}} \\
    \vspace{4pt}
    {\large \textbf{Computer Engineer \& Software Programming Technician}} \\
    \vspace{4pt}
    Mexico City, Mexico (GMT-6) \ | \ \href{mailto:contact@iamadbeltran.com}{contact@iamadbeltran.com} \\
    \href{https://github.com/iamadbeltran}{github.com/iamadbeltran} \ | \ \href{https://linkedin.com/in/iamadbeltran}{linkedin.com/in/iamadbeltran}
\end{center}

\vspace{6pt}

% PROFESSIONAL SUMMARY
\section{Professional Summary}
Passionate software developer with 7 years of practical coding experience since the age of 16. Candidate for a Bachelor of Science in Computer Engineering at UAM Azcapotzalco, built upon a solid vocational foundation as a certified Software Programming Technician. Highly skilled in backend development, data structures, and secure cloud operations. Proven track record of successful collaboration within agile development teams on complex technical integration projects. Fully bilingual with advanced communication skills certified at the C1.1 level.

% EDUCATION
\section{Education}
\noindent
\textbf{B.S. in Computer Engineering (Graduation Candidate)} \hfill 2022 -- Present \\
\textit{Universidad Autónoma Metropolitana (UAM Azcapotzalco)} \\
\begin{itemize}
    \item Currently finishing the final academic period. Expected Graduation: December 2026.
    \item Strong emphasis on systems engineering, computer networks, advanced algorithms, and data structures.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Technical Degree in Software Programming} \hfill 2019 -- 2022 \\
\textit{CECyT 9 ``Juan de Dios Bátiz'' -- Instituto Politécnico Nacional (IPN)} \\
\begin{itemize}
    \item Acquired a rigorous early technical foundation in object-oriented programming, logical system design, and databases.
    \item Graduated with full technical certification.
\end{itemize}

% PROJECTS & HIGHLIGHTS
\section{Technical Projects \& Highlights}
\noindent
\textbf{SDN University Integration Project (Lead Developer)} \hfill 2026 \\
\textit{UAM Azcapotzalco} \\
\begin{itemize}
    \item Designed and built a complex Software-Defined Network (SDN) topology to perform a rigorous comparative analysis between RSTP and OSPF routing protocols.
    \item Emulated production university network workloads using \textbf{Mininet} and customized automation logic scripted in \textbf{Python}.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Algorithmic Optimization \& Analysis} \hfill Ongoing \\
\textit{Personal Technical Log} \\
\begin{itemize}
    \item Consistently refactoring complex data structure challenges on LeetCode to achieve optimal execution speeds.
    \item Successfully optimized complex code blocks, reducing computational time complexity from $\mathcal{O}(N^2)$ down to linear time $\mathcal{O}(N)$ through the precise implementation of Hash Maps and efficient memory structures.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Secure Serverless Cloud Deployment} \hfill 2026 \\
\textit{Infrastructure Log} \\
\begin{itemize}
    \item Migrated personal portfolio infrastructure and production web environment to a high-availability architecture on \textbf{Cloudflare Pages}.
    \item Configured robust edge security policies and automated traffic filtering using Cloudflare's Web Application Firewall (\textbf{WAF}).
\end{itemize}

% TECHNICAL SKILLS
\section{Technical Skills}
\noindent
\begin{tabular}{@{}p{1.2in} p{5.2in}@{}}
    \textbf{Languages:} & Java, Python, C, C++, JavaScript (JS) \\
    \textbf{Databases:} & PostgreSQL, MySQL \\
    \textbf{Tools \& Cloud:} & Git, Cloudflare, Web Application Firewall (WAF), Mininet, SDN Topologies, Linux
\end{tabular}

% LANGUAGES & CERTIFICATIONS
\section{Languages \& Certifications}
\begin{itemize}
    \item \textbf{English:} Advanced Level C1.1 -- Certified by \textbf{goFluent} (Full professional proficiency, capable of working seamlessly with cross-border engineering teams).
    \item \textbf{Spanish:} Native speaker.
\end{itemize}

\end{document}